Security Audit of Safeplug

### 2014-01-14 results.tex
merge

\subsection{Teardown}
\label{sec:tear}

\subsubsection{Components}
    -Parts in the box

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.25\textwidth]{safeplug_top}
\caption{This is a figure.}
\end{center}
\end{figure}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.25\textwidth]{safeplug_bottom}
\caption{This is a figure.}
\end{center}
\end{figure}

>>>>

\subsection{Teardown}
\label{sec:tear}
We opened up the Safeplug device to look at the internals.  Figure~\ref{fig:top} shows the top of the board and Figure~\ref{fig:bottom} shows the bottom.  We identified an SD card slot, Lan transformer, and Ethernet transceiver on the top of the board.  On the bottom, we found flash memory and the integrated circuit.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.25\textwidth]{safeplug_top}
\caption{This is a figure.}
\label{fig:top}
\end{center}
\end{figure}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.25\textwidth]{safeplug_bottom}
\caption{This is a figure.}
\label{fig:bottom}
\end{center}
\end{figure}
